Fourmile Calibrations

### 2023-02-28 calibration_output.Rmd
updated for meeting
updated rd and rg plot sizes
things got weird
added LAI and fixed WDs

early_peakq <- ensem_bould %>%
  mutate(doy = yday(date)) %>%
  dplyr::select(c(doy, source, q_m3s, year)) %>%
  pivot_wider(names_from = 'source', values_from = c('q_m3s', 'doy'))

@@

```{r catch precip, echo = F}
setwd("C:/Users/sears/Documents/Repos/fourmile/catchment_output")

@@

```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
setwd("C:/Users/sears/Documents/Repos/fourmile/catchment_output")

gw_grid <- read_csv('gridall_outlet.csv') %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid')

gw_statn <- read_csv('statnall_outlet.csv') %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn')

@@

@@

hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
  dplyr::select(date, precip_mm, swe_mm) %>%
  rename(precip_mm_hrugrid = precip_mm,
         swe_mm_hrugrid = swe_mm)

hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
  dplyr::select(date, precip_mm, swe_mm) %>%
  rename(precip_mm_hrustatn = precip_mm,
         swe_mm_hrustatn = swe_mm)

@@

niwot_et <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/Niwot_daily_et.csv') %>%
  filter(year > 2010) %>%
  mutate(date = make_date(year = year, month = month, day = day)) %>%
  dplyr::select(date, et) %>%
  rename(et_niwot = et)

hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
  dplyr::select(date, AET_mm) %>%
  rename(et_hru7grid = AET_mm)

hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
  dplyr::select(date, AET_mm) %>%
  rename(et_hru7statn = AET_mm)

@@

tmean7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t7_grid = tmean)

tmean7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t7_statn = tmean)

tmean9_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_9_grid.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t9_grid = tmean)

tmean9_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_9_statn.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t9_statn = tmean)

tmean22_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_22_grid.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t22_grid = tmean)

tmean22_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_22_statn.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t22_statn = tmean)

tmean36_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_36_grid.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t36_grid = tmean)

tmean36_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_36_statn.csv') %>%
  dplyr::select(date, tmean) %>%
  rename(t36_statn = tmean)

@@

```{r cumulative tmean for HRUs, echo = F}
#grid first
setwd("C:/Users/sears/Documents/Repos/fourmile/HRU_output/grid")

@@

#statn next
setwd("C:/Users/sears/Documents/Repos/fourmile/HRU_output/statn")

@@

tmax_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll_prism.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmax_grid') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmax_mean_grid = mean(tmax_grid))

tmax_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmax_statn') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmax_mean_statn = mean(tmax_statn))

@@

tmax_grid_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll_prism.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmax_grid') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmax_grid = mean(tmax_grid))

tmax_statn_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmax_statn') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmax_statn = mean(tmax_statn))

@@

tmin_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll_prism.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_grid') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmin_mean_grid = mean(tmin_grid))

tmin_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_statn') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmin_mean_statn = mean(tmin_statn))

@@

```{r tmin month, echo = F}
tmin_grid_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll_prism.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_grid') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmin_grid = mean(tmin_grid))

tmin_statn_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_statn') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmin_statn = mean(tmin_statn))

@@

```{r tmax month, echo = F}
## Cumulative Precip difference

@@

reg_p <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_precipAll.csv',
                      skip = 21) %>%
  dplyr::select(-starts_with('@')) %>%
  mutate(time = dmy(time)) %>%
  summarize(across(`3`:`19`, ~ mean(.))) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'precip_avg') %>%
  mutate(value = as.numeric(value))

@@

>>>>

early_peakq <- ensem_bould %>%
  mutate(doy = yday(date)) %>%
  dplyr::select(c(doy, source, q_m3s, year)) %>%
  drop_na() %>% 
  pivot_wider(names_from = 'source', values_from = c('q_m3s', 'doy'))

@@

```{r catch precip, echo = F}
setwd("./catchment_output")

@@

```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}

gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid')

gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn')

@@

```{r gw boxplot, echo = F}

@@

hru7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>%
  dplyr::select(date, precip_mm, swe_mm) %>%
  rename(precip_mm_hrugrid = precip_mm,
         swe_mm_hrugrid = swe_mm)

hru7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>%
  dplyr::select(date, precip_mm, swe_mm) %>%
  rename(precip_mm_hrustatn = precip_mm,
         swe_mm_hrustatn = swe_mm)

@@

niwot_et <- read_csv(here('HRU_output/Niwot_daily_et.csv')) %>%
  filter(year > 2010) %>%
  mutate(date = make_date(year = year, month = month, day = day)) %>%
  dplyr::select(date, et) %>%
  rename(et_niwot = et)

hru7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>%
  dplyr::select(date, AET_mm) %>%
  rename(et_hru7grid = AET_mm)

hru7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>%
  dplyr::select(date, AET_mm) %>%
  rename(et_hru7statn = AET_mm)

@@

tmean7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>%
  dplyr::select(date, tmean) %>%
  rename(t7_grid = tmean)

tmean7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>%
  dplyr::select(date, tmean) %>%
  rename(t7_statn = tmean)

tmean9_grid <- read_csv(here('HRU_output/HRU_9_grid.csv')) %>%
  dplyr::select(date, tmean) %>%
  rename(t9_grid = tmean)

tmean9_statn <- read_csv(here('HRU_output/HRU_9_statn.csv')) %>%
  dplyr::select(date, tmean) %>%
  rename(t9_statn = tmean)

tmean22_grid <- read_csv(here('HRU_output/HRU_22_grid.csv')) %>%
  dplyr::select(date, tmean) %>%
  rename(t22_grid = tmean)

tmean22_statn <- read_csv(here('HRU_output/HRU_22_statn.csv')) %>%
  dplyr::select(date, tmean) %>%
  rename(t22_statn = tmean)

tmean36_grid <- read_csv(here('HRU_output/HRU_36_grid.csv')) %>%
  dplyr::select(date, tmean) %>%
  rename(t36_grid = tmean)

tmean36_statn <- read_csv(here('HRU_output/HRU_36_statn.csv')) %>%
  dplyr::select(date, tmean) %>%
  rename(t36_statn = tmean)

@@

```{r cumulative tmean for HRUs, echo = F}
#grid first
setwd(here("HRU_output/grid"))

@@

#statn next
setwd(here("HRU_output/statn"))

@@

tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmax_grid') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmax_mean_grid = mean(tmax_grid))

tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmax_statn') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmax_mean_statn = mean(tmax_statn))

@@

tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmax_grid') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmax_grid = mean(tmax_grid))

tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmax_statn') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmax_statn = mean(tmax_statn))

@@

tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_grid') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmin_mean_grid = mean(tmin_grid))

tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_statn') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmin_mean_statn = mean(tmin_statn))

@@

```{r tmin month, echo = F}
tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_grid') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmin_grid = mean(tmin_grid))

tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_statn') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmin_statn = mean(tmin_statn))

@@

## Cumulative Precip difference

@@

reg_p <- read_csv(here('HRU_output/reg_precipAll.csv'),
                      skip = 21) %>%
  dplyr::select(-starts_with('@')) %>%
  mutate(time = dmy(time)) %>%
  summarize(across(`3`:`19`, ~ mean(.))) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'precip_avg') %>%
  mutate(value = as.numeric(value))

@@

## Average LAI comparison

```{r lai, echo = F}

#get rid of a bunch of data
hru_grid_LAI <- hru_grids %>%
  dplyr::select(c(time, ID, LAI)) %>%
  rename(LAI_grid = LAI)  %>%
  group_by(ID) %>%
  summarize(LAI_all_grid = mean(LAI_grid))

hru_statn_LAI <- hru_statn %>%
  dplyr::select(c(time, ID, LAI)) %>%
  rename(LAI_statn = LAI) %>%
  group_by(ID) %>%
  summarize(LAI_all_statn = mean(LAI_statn))

LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>%
  rename(value = ID)

hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value')

LAIavg_grid <- tm_shape(hrus_map_LAI) +
  tm_polygons('LAI_all_grid', midpoint = NA, id = 'value',
              breaks = c(1,2,3,4,5)) +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average LAI')

LAIavg_statn <- tm_shape(hrus_map_LAI) +
  tm_polygons('LAI_all_statn', midpoint = NA, id = 'value',
              breaks = c(1,2,3,4,5)) +
  tm_legend(legend.outside = T)

tmap_arrange(LAIavg_grid, LAIavg_statn)
